\clearpage
\addcontentsline{toc}{section}{References}
\begin{thebibliography}{99}
\bibitem{b1}\emph{"Quantised Singularities in the Electromagnetic Field"} by  Paul Dirac. Proc. Roy. Soc. (London) A 133, 60 (1931)
\bibitem{b2}\emph{"Evidence for Detection of a Moving Magnetic Monopole"} by P. B. Price; E. K. Shirk; W. Z. Osborne; L. S. Pinsky. (August 25, 1975) Physical Review Letters (American Physical Society) 35 (8): 487–490.
\bibitem{b3}\emph{"First Results from a Superconductive Detector for Moving Magnetic Monopoles"} by  Blas Cabrera. (May 17, 1982) Physical Review Letters (American Physical Society) 48 (20): 1378–1381.
\bibitem{b4}\emph{"Theoretical and experimental status of magnetic monopoles"} by Kimball A. Milton. (June 2006) Reports on Progress in Physics 69 (6): 1637–1711
\bibitem{b5}\emph{"Molecular Rotation in Ice at 10K. Free Energy of Formation and Entropy of Water"} by W.F. Giauque \& M.F. Ashley. Phys. Rev. 43, 81 (1933).
\bibitem{b6}\emph{"The Structure and Entropy of Ice and of Other Crystals with Some Randomness of Atomic Arrangement"} by L. Pauling.  J. Chem. Phys. 57, 2680 (1935).
\bibitem{b7}\emph{"The Structure and residual entropy of ice."} by R.E. Rundle. 1953 J. chem. Phys. 21 1311
\bibitem{b8}\emph{"The Structure of Ice"} by R.E. Rundle. Journal of Phys Chem 59 680-2
\bibitem{b9}\emph{"The structure of ice I$_{h}$"} by W. F. Kuhs and M. S. Lehmann. Water Science Reviews 2 (Cambridge University Press: 1986) pp. 1-66.
\bibitem{b10}\emph{"Ordering and Antiferromagnetism in Ferrites"} by P.W. Anderson. Phys. Rev. 102, 1008 (1956).
\bibitem{b11}\emph{"Geometrical Frustration in the Ferromagnetic Pyrochlore Ho$_{2}$Ti$_{2}$O$_{7}$"} by M.J. Harris et al. Phys. Rev. Lett. 79, 2554 (1997).
\bibitem{b12}\emph{"Zero-point entropy in 'spin ice'."} by A.P. Ramirez et al. Nature 399, 333 (1999).
\bibitem{b13}\emph{"Artificial ‘spin ice’ in a geometrically frustrated lattice of nanoscale ferromagnetic islands"} by R. F. Wang, C. Nisoli, R. S. Freitas, J. Li, W. McConville, B. J. Cooley, M. S. Lund, N. Samarth, C. Leighton,V. H. Crespi \& P. Schiffer Nature 439, 303-306 (19 January 2006)
\bibitem{b14}\emph{"Emerging Chirality in Artificial Spin Ice"} by  W.R. Branford et al. Science 335,1597 (2012).
\bibitem{b15}\emph{"Real-space observation of emergent magnetic monopoles and associated Dirac strings in artificial kagome spin ice"} by Elena Mengotti, Laura J. Heyderman, Arantxa Fraile Rodríguez, Frithjof Nolting, Remo V. Hügli and Hans-Benjamin Braun. Nature Physics Vol 7 January 2011
\bibitem{b16}\emph{"Spin Ice State in Frustrated Magnetic Pyrochlore Materials"} by Steven T. Bramwell1, Michel J. P. Gingras. Science 16 November 2001: Vol. 294 no. 5546 pp. 1495-1501 DOI: 10.1126/science.1064761
\end{thebibliography}
